Refinements for open automata

### 2022-06-16 2021-Refinement/paper/refinementarticle.tex
R'

Consider one $t_{1x}=\OT{s_1}{s_{1x}}{\alpha_{1x}}{\beta_{1xj}^{j \in J'_{1x}}}{g_{1x}}{\psi_{1x}}\in \fOT{s_1}$ to obtain a new open transition of A1 and compose it with $t_3^2$

We obtain 
\[
t_{13x}' = \OT{\mpar{s_1, s_3}}{\mpar{s_{1x}, {s_3}}}{\alpha_{1x}}{\beta_{1xj}^{j \in J'_{1x} \setminus \{k\}} \uplus  {(\beta^2_{3j})^{j \in J^{2 \prime}_3} }}{g_{1x} \wedge g^2_3 \wedge \alpha^2_3 = \beta_{1xk}}{\psi_{1x} \uplus \psi^2_3} \qquad \text{ where } k \in J'_{1x} 
\]

This specifies the family $\mpar{t_{13x}'}^{x\in X}$
that allows us to prove the initial goal, i.e. the relation is preserved along identical transitions. We derive from the property ($\star$) and from the definition of $t_{13x}'$ and $t_{23}$
\begin{multline*}
  V_{13} \uplus V_{23} \uplus  \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} 
\vdash \hspace{6cm}\\  R\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} 
\implies 
 R\mpar{s_{1}, s_{2}} \wedge 	g_{1} \wedge g_2 \wedge g^2_3 \wedge \alpha^2_3 = \beta_{2k} \wedge \alpha_{1} = \alpha_{2} 
\end{multline*}

\begin{multline*}
  V_{13} \uplus V_{23} \uplus  \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} 
\vdash \hspace{6cm}\\  R\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} 
\implies 
\bigwedge_{x\in X}
\big(
 \alpha_{13}=\alpha_1=\alpha_{1 x}  \land J'_{1x}\uplus J'_3= J'_2\uplus J'_3\\
 \land \bigwedge_\subbox{j \in J'_2 \setminus\{k\} } \beta_{2j} = \beta_{1xj}
 \land \bigwedge_\subbox{j \in {j \in J^{2 \prime}_3} }  (\beta^2_{3j}) = (\beta^2_{3j}) \land g_{1 x}\land
 R\mpar{s'_{1 3x}, s'_{23}}\psubst{\psi_{1 x} \uplus \psi_2}\big)
\wedge g^2_3 \wedge \alpha^2_3 = \beta_{2k} = \beta_{1xk}
\end{multline*}
Finally , because $R\mpar{s'_{1 3x}, s'_{23}}\psubst{\psi_{1 x} \uplus \psi_2} \implies R\mpar{s'_{1 3x}, s'_{23}}\psubst{(\psi_{1 x} \uplus \psi^2_3) \uplus (\psi_2 \uplus \psi^2_3)}$
\begin{multline*}
  V_{13} \uplus V_{23} \uplus  \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} 
\vdash \hspace{6cm}\\  R\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} 
\implies \\
\bigwedge_{x\in X}
\mpar{
 \alpha_{13}=\alpha_{1 3x} \land
J'_{13x}  = J'_{23}  \land \bigwedge_\subbox{j \in  J'_{23}} \beta_{23j} = \beta_{13xj}\land g_{1 3x} \land
 R\mpar{s'_{1 3x}, s'_{23}}\psubst{\psi_{1 3x} \uplus \psi_{23}}}
\end{multline*}

>>>>

Consider one $t_{1x}=\OT{s_1}{s_{1x}}{\alpha_{1x}}{\beta_{1xj}^{j \in J'_{1x}}}{g_{1x}}{\psi_{1x}}\in \fOT{s_1}$ to obtain a new open transition of A1 and compose it with $t_3^2$.
We obtain 
\[
t_{13x}' = \OT{\mpar{s_1, s_3}}{\mpar{s_{1x}, {s_3}}}{\alpha_{1x}}{\beta_{1xj}^{j \in J'_{1x} \setminus \{k\}} \uplus  {(\beta^2_{3j})^{j \in J^{2 \prime}_3} }}{g_{1x} \wedge g^2_3 \wedge \alpha^2_3 = \beta_{1xk}}{\psi_{1x} \uplus \psi^2_3} \qquad \text{ where } k \in J'_{1x} 
\]

This specifies the family $\mpar{t_{13x}'}^{x\in X}$
that allows us to prove the initial goal, i.e. the relation is preserved along identical transitions. We derive from the property ($\star$) and from the definition of $t_{13x}'$ and $t_{23}$
\begin{multline*}
  V_{13} \uplus V_{23} \uplus  \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} 
\vdash \hspace{6cm}\\  R'\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} 
\implies \\
 R\mpar{s_{1}, s_{2}} \wedge 	g_{1} \wedge g_2 \wedge g^2_3 \wedge \alpha^2_3 = \beta_{2k} \wedge \alpha_{1} = \alpha_{2} \bigwedge_\subbox{v_3\in V_3}
 v^1_3=v^2_3\wedge s^1_3 = s^2_3
\end{multline*}

\begin{multline*}
  V_{13} \uplus V_{23} \uplus  \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} 
\vdash \hspace{6cm}\\  R'\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} 
\implies 
\bigwedge_{x\in X}
\big(
 \alpha_{13}=\alpha_1=\alpha_{1 x}  \land J'_{1x}\uplus J'_3= J'_2\uplus J'_3\\
 \land \bigwedge_\subbox{j \in J'_2 \setminus\{k\} } \beta_{2j} = \beta_{1xj}
 \land \bigwedge_\subbox{j \in {j \in J^{2 \prime}_3} }  (\beta^2_{3j}) = (\beta^2_{3j}) \land g_{1 x}\land
 R'\mpar{s'_{1 3x}, s'_{23}}\psubst{\psi_{1 x} \uplus \psi_2}\big)
\wedge g^2_3 \wedge \alpha^2_3 = \beta_{2k} = \beta_{1xk}
\end{multline*}
Finally , because $R'\mpar{s'_{1 3x}, s'_{23}}\psubst{\psi_{1 x} \uplus \psi_2} \implies R\mpar{s'_{1 3x}, s'_{23}}\psubst{(\psi_{1 x} \uplus \psi^2_3) \uplus (\psi_2 \uplus \psi^2_3)}$
\begin{multline*}
  V_{13} \uplus V_{23} \uplus  \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} 
\vdash \hspace{6cm}\\  R'\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} 
\implies \\
\bigwedge_{x\in X}
\mpar{
 \alpha_{13}=\alpha_{1 3x} \land
J'_{13x}  = J'_{23}  \land \bigwedge_\subbox{j \in  J'_{23}} \beta_{23j} = \beta_{13xj}\land g_{1 3x} \land
 R'\mpar{s'_{1 3x}, s'_{23}}\psubst{\psi_{1 3x} \uplus \psi_{23}}}
\end{multline*}
